My Cool Title

### 2019-05-05 paper.tex
Started adding object detector description and references

\todo{Object detectors}

@@

>>>>

Object detectors can be divided into two main categories that use single-stage and 2-stage methods.  
The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects. 
They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements.\todo{cite}
On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
This leads to model that uses much less memory, but again with a small drop in accuracy.

@@

The SSD-Lite network is a single-stage object detection network that is based on the SSD architecture, but uses MobileNetV2\todo{cite} for its backbone.
This leads to a more `lightweight' model that has less parameters and requires less memory to perform inference tasks, which makes it suitable for a mobile platform. 
This model achieves a mAPs of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset~\cite{lin2014microsoft}. 
When compared with the full SSD model, it achieves a slightly lower mAPs (0.25), but with significantly less parameters (34.3M) and FLOPS (34.36B).
\todo{compare with alterniative}
